%-------------------------
% Resume in Latex
% Author : Vaibhav Jain
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{fontawesome}
\usepackage{multicol}
% \usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Vaibhav Jain} \\ \vspace{1pt}
    Delhi, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8377044667 ~ \href{mailto:vaibhavjain301999@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{vaibhavjain301999@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/vaibhav-j-868333113/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/vaibhav-j-868333113}}  ~
    \href{https://github.com/vaibhav3099}
    {\raisebox{-0.2\height}\faGithub\ \underline{github.com/vaibhav3099}}
    {\raisebox{-0.2\height}\faBlog\ \textcolor{blue}{\underline{https://medium.com/@vaibhavjain301999}}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}

\resumeSubHeadingListStart
\resumeItemListStart

\resumeItem{\textbf{SaaS Expertise} - Built E-signature modules, Full scale Employee ERP systems, HR \& Payroll Management System, Sports League Management Platform etc.
}
\resumeItem{\textbf{AI Leverage} - Established clear architectural rules and coding patterns that enable developers deliver features faster.}

\resumeItem{\textbf{Architectural Ownership} - Have owned end-to-end projects, from system design to delivery.
}

\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

% ----- changes
\resumeSubheading{Open Source Contributions}{Present}{}{}
\resumeItemListStart
\resumeItem{
\textbf{Obsidian - Spaced Repetition} - \href{https://github.com/st3v3nmw/obsidian-spaced-repetition/pull/1585}{\textcolor{blue}{\underline{feat: Enhance review notes sidebar}}}
\newline - Problem: Poor visibility of overdue and due-today notes in large, nested review hierarchies.
\newline - Action: Implemented status propagation and visual indicators at file and folder levels to surface note states at a glance.
\newline - Improved navigation efficiency and reduced effort required to manage large review trees.}
\resumeItemListEnd
%---- changes end



\resumeSubheading{SpotDraft}{May 2022 -- Feb 2023}{Senior Frontend Engineer | \textit{Angular, Typescript, SCSS, Clean Architecture}}{Bangalore}
\resumeItemListStart
\resumeItem{
\textbf{E-Signature Module} - \href{https://drive.google.com/file/d/1mk2LK5-s5LVKd_3G_H5tf5gIsxwKz5Bf/view}{\textcolor{blue}{\underline{workflow demo}}}
\newline - Problem: Existing signing workflows were not optimized for small screen devices, thus customer experience was not seamless.
\newline - Action: Re-architected the signing workflows using modular architecture with modern mobile-first approach.
\newline - Business Impacts: Strengthened the product's competitive positioning by delivering a modern mobile-device signing experience expected from enterprise e-signature solutions.



\resumeItem{\textbf{Embeddable App for PDF Signing}
\newline - Problem:  Customers could not offer contract signing within their own products and had to redirect users to SpotDraft.
\newline - Action: Built an embeddable PDF signing application, enabling customers to integrate signing workflows into their own platforms.
\newline - Business Impact: Unlocked new integration use cases for customers. A high-value customer requested this feature which it got saved from churning.
}

\resumeItem{
\textbf{Signature Packets}
\newline - Problem: Users had to manage multiple contracts separately when handling multiple uploads.
\newline - Action: Developed Signature Packets feature to generate a unified contract from multiple uploads
\newline - Business Impact:  Hassle of managing each individual contract is resolved. 
}

\resumeItem{
\textbf{Code Quality and Standards}
\newline - Problem: Code quality and review standards varied across the team.
\newline - Action: Led code quality initiatives through rigorous code reviews, established PR standards.
\newline - Engineering Impacts: Standardized engineering consistency, reduced review friction.
}
}
\resumeItemListEnd

\resumeSubheading{Unthinkable Solutions}{July 2020 -- Feb 2022}{Full Stack Developer | Angular, React, Typescript, NodeJS, Express, PostgreSQL}{Gurugram}
\resumeItemListStart
\resumeItem{

\textbf{Sports League Management System}
\newline - Requirement: A Sport organization needed a centralized platform to manage leagues, teams, fixtures, referees with all features from Scheduling to Payments.
\newline - Ownership: Worked as Solo Contributor, owned the project end to end until delivery, be it full stack development, architecture, client interaction, on-call issues and everything in between.
\newline - Results: Developed key features - Match Scheduling, Refrees Payments, Notifications and Emailing, Batch updates etc.
}
\resumeItem{
\textbf{HR Management System}
\newline - Problem: Duplicated Data-tables implementations across modules.
\newline - Action: Created \textbf{In-House Data-grid }from scratch, with configurable columns, cells using parser callbacks similar to ag-grid 
\href{https://www.ag-grid.com/}{\faExternalLink}
\newline - Impact: Enabled plug-and-play adoption across 10+ modules, faster feature delivery and reduced testing overhead.
}

\resumeItem{
\textbf{Authentication and Permission Handling}
\newline - Problem: As the application grew, managing user access across different roles became complex
\newline - Action: Implemented a centralized authentication and authorization system using JWT, Access/Refresh Tokens, Redis, Express middlewares, RBAC, Route Guards, and permission-based UI grid
\newline - Business Impact: Superadmin now can hide or enable different features to different type of users, as per business requirements.
}
\resumeItemListEnd

\resumeSubheading{TDG Labs}{Jan 2020 -- July 2020 }{Software Engineer | \textit{React, Redux, Material UI (MUI)}}{Delhi}
\resumeItemListStart

\resumeItem{
\textbf{In-house UI Library}
\newline- Problem: Fragmented UX due to inconsistent UI across the application. Client required consistent UI components on Material Theme.
\newline- Action: Built a shared component library by customizing MUI primitives such as Buttons, Modals, Forms, Dropdowns etc.
\newline- Business Impact: Consistent UI across all modules. Enabled faster feature delivery
}

\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------TECH STACK-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: Javascript, Typescript, HTML/CSS, SCSS/SASS, SQL} \\
\textbf{Architecture}{: Clean Architecture, Nx Monorepos} \\
\textbf{Frontend}{: React, Redux, Angular, RxJs, NgRx, TestBed, RESTful APIs, Lazy loading, Angular Material, Bootstrap, MUI, Tailwind, Responsive Web Design, Storybook} \\
\textbf{Backend}{: NodeJs, Express.js, PostgreSQL (knex), REST API development, Authentication (JWT), RBAC} \\
\textbf{DevOps}{: Docker, CI/CD (GitHub Actions, GitLab CI, JIRA), Nginx, PM2} \\
\textbf{Analytics}{: Datadog, Amplitude} \\
\textbf{Version Control \& Tools}{: npm, Git, GitHub, GitLab, Bitbucket, Jira, Trello, Figma, ESLint, Prettier, Husky, Swagger (OpenAPI)} \\
}}
\end{itemize}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Guru Gobind Singh Indraprastha University}{2016 -- 2020}{Bachelor of Technology in Computer Science CGPA - 9.34}{Delhi, India}
\item{\textbf{CGPA | 9.34} [University top 10 list]}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeSubHeadingListStart
\resumeSubheading{\href{https://drive.google.com/drive/u/1/folders/1dMF82uPbvHjp7ZFfwgRY36duLTu1IO10}{\textcolor{blue}{\underline{Outstanding Delivery Award \faExternalLink}}}}{Nov 2020}{Delivered MatchRider in just 4 months, appreciated for aligning with business needs.}{}
\resumeSubheading{\href{https://drive.google.com/drive/folders/1kl8TmB8SaVZ5YwXo8xHsloigwAdjzRR5}{\textcolor{blue}{\underline{Engineering Impact Testimonials \faExternalLink}}}}{May 2022 -- Feb 2023}{Elevated engineering quality by establishing code review and development standards.}{}
\resumeSubHeadingListEnd

\end{document}
